Embedded Domain-Specific Languages:\\ Composable Interpretations with Dependencies

### 2015-03-29 paper/Main.tex
Starting on MRM

\section{Introduction}

@@

Following is the construction of the Brent-Kung parallel prefix circuit:

\begin{verbatim}
c1 :: Circuit circuit => circuit
c1 = (fan 2 `beside` fan 2) `above`
     stretch [2,2] (fan 2) `above`
     (identity 1 `beside` fan 2 `beside` identity 1)
\end{verbatim}

@@

Then we can use the above functions to get  different properties of c1, depending on its type. For example, \textit{gwidth (c1 :: Compose Width Depth)} and \textit{gdepth (c1 :: Compose Width Depth)} will give us its width and depth,  respectively.

@@

For composition, we introduce the operator (\textbf{$<$+$>$}), which takes two algebras as inputs and gives back an algebra that returns a composed type:

@@

>>>>

\section{Introduction}
% Basic approach without dependency or composition. F-Algebra for deep embedding.

@@

Following is a flexibly typed Brent-Kung parallel prefix circuit:

\begin{verbatim}
c2 :: Circuit circuit => circuit
c2 = (fan 2 `beside` fan 2) `above`
     stretch [2,2] (fan 2) `above`
     (identity 1 `beside` fan 2 `beside` identity 1)
\end{verbatim}

@@

Then we can use the above functions to get  different properties of c2, depending on its type. For example, \textit{gwidth (c1 :: Compose Width Depth)} and \textit{gdepth (c2 :: Compose Width Depth)} will give us its width and depth,  respectively.

@@

For composition, we introduce the operator (\textbf{$<+>$}), which takes two algebras as inputs and gives back an algebra that returns a composed type:

@@

An algebra that returns \textit{Compose Width WellSized} is simply:
\begin{verbatim}
cAlg2 = widthAlg <+> wsAlg
\end{verbatim}

Then we can evaluate circuit c1 defined earlier and get its width by:
\begin{verbatim}
gwidth (fold cAlg2 c1)
\end{verbatim}

And check whether it is well-formed or not by:
\begin{verbatim}
gwellSized (fold cAlg2 c1)
\end{verbatim}
